Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-11-11 paper.tex
More related work

>>>>

\subsection{Other frameworks}

A large number of frameworks have been created to facilitate the
integration of command-line applications in platforms. In
neuroinformatics, several platforms platforms define a formal
interface to embed command-line applications. Among them, the Common
Toolkit\footnote{\url{http://www.commontk.org}} has an
interoperability focus like \boutiques as its command-line modules are
supported by several platforms such as 3D Slicer~\cite{pieper20043d},
NiftyView~\cite{Craddock2016}, GIMIAS~\cite{larrabide2009gimias},
MedInria~\cite{larrabide2009gimias}, MeVisLab~\cite{heckel2009object}
and MITK workbench~\cite{nolden2013medical}. The framework, however,
remains tightly bound to the Common Toolkit's C++ implementation which
limits its adoption, e.g., in web platforms \todo{Fr\'ed\'eric, maybe
  you have more to say on this}.

In the distributed computing community, systems were also proposed to
facilitate the embedding of applications in platforms. The Grid
Execution Management for Legacy Code Architecture
(GEMLCA~\cite{delaitre2005gemlca}) was used to wrap applications in
grid computing systems. Interestingly, it has been used to embed
workflow engines in the SHIWA
platform~\cite{terstyanszky2014enabling}, in a similar but different
way than proposed by \boutiques (Section~\ref{sec:parallelization}).

The recent advent of virtual containers requires a new generation of
application description frameworks that are independent from any
programming language and that expose a rich set of properties to
describe command lines as intended by \boutiques.
